Practical Optional Types for Clojure

### 2016-01-13 intro.tex
WIP grayscale

\begin{figure}[t!]
\inputminted[firstline=15]{clojure}{code/demo/src/demo/ex-intro.clj}
\caption{A simple Typed Clojure program}
\label{fig:ex1}
\end{figure}

>>>>

\begin{figure*}[t!]
\begin{lstlisting}
(ann pname [(U File String) -> (U nil String)])
(defmulti pname class)  ; multimethod dispatching on class of argument
(defmethod pname String [s] (pname (new File s))) ; String case 
(defmethod pname File [f] (.getName f)) ; File case, with static null check
(pname "STAINS/JELLY") ;=> "JELLY" :- (U nil Str)
\end{lstlisting}
\caption{A simple Typed Clojure program}
\label{fig:ex1}
\end{figure*}
